Supporting Information

### 2021-10-27 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
new run

#prepare a dataset
df_rob <- rob_records %>%
  select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
         risk_of_bias_update_3_complete)
df_rob['setting'] <- NA

@@

#Filtered by Q1
q1_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(quest___1 == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, D6 = rob_6)

q1_rob$D1 <- ifelse(q1_rob$D1 == 1, "High", ifelse(q1_rob$D1 == 2, "Unclear", "Low"))
q1_rob$D2 <- ifelse(q1_rob$D2 == 1, "High", ifelse(q1_rob$D2 == 2, "Unclear", "Low"))
q1_rob$D3 <- ifelse(q1_rob$D3 == 1, "High", ifelse(q1_rob$D3 == 2, "Unclear", "Low"))
q1_rob$D4 <- ifelse(q1_rob$D4 == 1, "High", ifelse(q1_rob$D4 == 2, "Unclear", "Low"))
q1_rob$D5 <- ifelse(q1_rob$D5 == 1, "High", ifelse(q1_rob$D5 == 2, "Unclear", "Low"))
q1_rob$D6 <- ifelse(q1_rob$D6 == 1, "High", ifelse(q1_rob$D6 == 2, "Unclear", "Low"))

@@

#1. "Contact investigation" and "Contact investigation, aggregated"
contactinvestigation <- q1_rob %>% 
  filter(setting == "Contact investigation" | setting == "Contact investigation, aggregated") %>%
  select(Study, D1, D2, D3, D4, D5, D6)

@@

# 3. "Outbreak investigation"
outbreakinv <- q1_rob %>% 
  filter(setting == "Outbreak investigation") %>%
  select(Study, D1, D2, D3, D4, D5, D6)

@@

# 9. "Screening: institutional setting"
institutional <- q1_rob %>% 
  filter(setting == "Screening: institutional setting") %>%
  select(Study, D1, D2, D3, D4, D5, D6)
#Records: 21 studies

@@

# 10. "Screening: community setting"
communityset <- q1_rob %>% 
  filter(setting == "Screening: community setting") %>%
  select(Study, D1, D2, D3, D4, D5, D6)
#Records: 17 studies

@@

# 11. "Screening: occupational"
occupationalset <- q1_rob %>% 
  filter(setting == "Screening: occupational") %>%
  select(Study, D1, D2, D3, D4, D5, D6)
#Records: 12 studies

@@

    Selection Bias:
  D1.1: Representativeness of the sample
  D1.2: Characteristics of non-respondents
    Information Bias:
  D2.1: Symptom assessment
  D2.1: Recording of symptoms
    Misclassification bias:
  D3: Classification of asymptomatic status
    Attrition bias:
  D4: Selective reporting of symptoms status")

@@

###ROB analysis for Q2.1
q2_rob <- df_rob %>%
  filter(q3_sar == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, D6 = rob_6)

q2_rob$D1 <- ifelse(q2_rob$D1 == 1, "High", ifelse(q2_rob$D1 == 2, "Unclear", "Low"))
q2_rob$D2 <- ifelse(q2_rob$D2 == 1, "High", ifelse(q2_rob$D2 == 2, "Unclear", "Low"))
q2_rob$D3 <- ifelse(q2_rob$D3 == 1, "High", ifelse(q2_rob$D3 == 2, "Unclear", "Low"))
q2_rob$D4 <- ifelse(q2_rob$D4 == 1, "High", ifelse(q2_rob$D4 == 2, "Unclear", "Low"))
q2_rob$D5 <- ifelse(q2_rob$D5 == 1, "High", ifelse(q2_rob$D5 == 2, "Unclear", "Low"))
q2_rob$D6 <- ifelse(q2_rob$D6 == 1, "High", ifelse(q2_rob$D6 == 2, "Unclear", "Low"))

q2_plot_ds <- q2_rob %>% 
  select(Study, D1, D2, D3, D4, D5, D6)

@@

dev.new()
png("q2_new.png", width = 1000, height = 300)
p8
graphics.off()

>>>>

#prepare a dataset
# df_rob <- rob_records %>%
#   select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
#          rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
#          risk_of_bias_update_3_complete)

df_rob <- rob_records %>%
  select(record_id,author_1, quest___1, q3_sar, setting2, 
         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
         risk_of_bias_update_3_complete)
df_rob['setting'] <- NA

@@

#Filtered by Q1
q1_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(quest___1 == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, `6` = rob_6)

q1_rob$D1 <- ifelse(q1_rob$D1 == 1, "High", ifelse(q1_rob$D1 == 2, "Unclear", "Low"))
q1_rob$D2 <- ifelse(q1_rob$D2 == 1, "High", ifelse(q1_rob$D2 == 2, "Unclear", "Low"))
q1_rob$D3 <- ifelse(q1_rob$D3 == 1, "High", ifelse(q1_rob$D3 == 2, "Unclear", "Low"))
q1_rob$D4 <- ifelse(q1_rob$D4 == 1, "High", ifelse(q1_rob$D4 == 2, "Unclear", "Low"))
q1_rob$D5 <- ifelse(q1_rob$D5 == 1, "High", ifelse(q1_rob$D5 == 2, "Unclear", "Low"))
q1_rob$`6` <- ifelse(q1_rob$`6` == 1, "High", ifelse(q1_rob$`6` == 2, "Unclear", "Low"))

@@

#1. "Contact investigation" and "Contact investigation, aggregated"
contactinvestigation <- q1_rob %>% 
  filter(setting == "Contact investigation" | setting == "Contact investigation, aggregated") %>%
  select(Study, D1, D2, D3, D4, D5, `6`)

@@

# 3. "Outbreak investigation"
outbreakinv <- q1_rob %>% 
  filter(setting == "Outbreak investigation") %>%
  select(Study, D1, D2, D3, D4, D5, `6`)

@@

# 9. "Screening: institutional setting"
institutional <- q1_rob %>% 
  filter(setting == "Screening: institutional setting") %>%
  select(Study, D1, D2, D3, D4, D5, `6`)
#Records: 21 studies

@@

# 10. "Screening: community setting"
communityset <- q1_rob %>% 
  filter(setting == "Screening: community setting") %>%
  select(Study, D1, D2, D3, D4, D5, `6`)
#Records: 17 studies

@@

# 11. "Screening: occupational"
occupationalset <- q1_rob %>% 
  filter(setting == "Screening: occupational") %>%
  select(Study, D1, D2, D3, D4, D5, `6`)
#Records: 12 studies

@@

    Selection Bias:
  1: Representativeness of the sample
  2: Characteristics of non-respondents
    Information Bias:
  3: Symptom assessment
  4: Recording of symptoms
    Misclassification bias:
  5: Classification of asymptomatic status
    Attrition bias:
  6: Selective reporting of symptoms status")

@@

###ROB analysis for Q2.1
q2_rob <- df_rob %>%
  filter(q3_sar == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, `6` = rob_6)

q2_rob$D1 <- ifelse(q2_rob$D1 == 1, "High", ifelse(q2_rob$D1 == 2, "Unclear", "Low"))
q2_rob$D2 <- ifelse(q2_rob$D2 == 1, "High", ifelse(q2_rob$D2 == 2, "Unclear", "Low"))
q2_rob$D3 <- ifelse(q2_rob$D3 == 1, "High", ifelse(q2_rob$D3 == 2, "Unclear", "Low"))
q2_rob$D4 <- ifelse(q2_rob$D4 == 1, "High", ifelse(q2_rob$D4 == 2, "Unclear", "Low"))
q2_rob$D5 <- ifelse(q2_rob$D5 == 1, "High", ifelse(q2_rob$D5 == 2, "Unclear", "Low"))
q2_rob$`6` <- ifelse(q2_rob$`6` == 1, "High", ifelse(q2_rob$`6` == 2, "Unclear", "Low"))

q2_plot_ds <- q2_rob %>% 
  select(Study, D1, D2, D3, D4, D5, `6`)

@@

dev.new()
png("q2_new.png", width = 1000, height = 350)
p8
graphics.off()
